\begingroup 
\renewcommand{\section}[2]{\anonsection{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ И ЛИТЕРАТУРЫ}}
\begin{flushleft}
\begin{thebibliography}{}

\bibitem{C4collector}
Gil Tene, Balaji Iyengar, Michael Wolf. C4: The Continuously Concurrent Compacting Collector
  // ACM SIGPLAN Notices. --- 2011. --- Vol. 46, No. 11. --- P. 79-88.

\bibitem{type-system}
Types and Programming Languages / Benjamin C. Pierce // The MIT Press, --- 2002.
	%https://theswissbay.ch/pdf/Gentoomen%20Library/Maths/Comp%20Sci%20Math/Benjamin_C._Pierce-Types_and_Programming_Languages-The_MIT_Press%282002%29.pdf

\bibitem{java-spec}
Gosling, J., Joy, B., Steele, G., Bracha, G., Buckley, A. The Java Language
Specification. Java SE 8 Edition. --- 2015. --- Oracle America, Inc.

\bibitem{jvm-spec}
Lindholm, T., Yellin, F., Bracha, G., Buckley, A. The Java Virtual Machine
Specification. Java SE 8 Edition. --- 2015. --- Oracle America, Inc.
	
\bibitem{wimmer-field-inlining}
Christian Wimmer. Automatic Object Inlining in a Java Virtual Machine. --- 2008. --- Institute for System Software
Johannes Kepler University Linz.

\bibitem{jmh}
Java Microbenchmark Harness. [Электронный ресурс]. --- 2022. --- URL: https://openjdk.org/projects/code-tools/jmh/
	
\bibitem{llvm-ref-man}
LLVM Language Reference Manual. [Электронный ресурс]. --- 2022. --- URL: https://llvm.org/docs/LangRef.html
	
\bibitem{ssa-book}
Static Single Assignment Book. [Электронный ресурс]. --- 2022. --- URL: https://pfalcon.github.io/ssabook/latest/book-full.pdf
	
\bibitem{gc-handbook}
The Garbage Collection Handbook: The Art of Automatic Memory Management / Chapman \& Hall, 2012 // CRC Press. --- 2012.
	
\bibitem{gc-llvm}
Garbage Collection with LLVM. [Электронный ресурс]. --- 2023. --- URL: https://llvm.org/docs/GarbageCollection.html
	
\bibitem{falcon-gil}
Gil Tene. Zing hits the trifecta. [Электронный ресурс]. --- 2017. --- URL: https://stuff-gil-says.blogspot.com/2017/

\bibitem{C4-perf}
Azul C4 Garbage Collector. [Электронный ресурс]. --- 2023. --- URL: https://www.azul.com/products/components/pgc/

\bibitem{llvm-arch}
Chris Lattner. The Architecture of Open Source Applications (Volume 1). [Электронный ресурс]. --- 2023. --- URL: LLVM https://aosabook.org/en/v1/llvm.html

\bibitem{gil-gc-latency}
Gil Tene on Zing, Low Latency GC, Responsiveness. [Электронный ресурс]. --- 2017. --- URL: https://www.infoq.com/interviews/tene-low-latency/

\bibitem{spec98}
The SPECjvm98 Benchmarks. [Электронный ресурс]. --- 2008 . --- URL: http://www.spec.org/jvm98

\bibitem{valhalla}
Project Valhalla.  [Электронный ресурс]. --- 2022 . --- URL: http://www.spec.org/jvm98 https://openjdk.org/projects/valhalla/

\bibitem{valhalla-value-object}
JEP draft: Value Objects (Preview). [Электронный ресурс]. --- 2023. --- URL: https://openjdk.org/jeps/8277163

\bibitem{contained-obj}
org.ObjectLayout. [Электронный ресурс]. --- 2023. --- URL: http://objectlayout.github.io/ObjectLayout/

\end{thebibliography}
\end{flushleft}
\endgroup

\clearpage
